Papers

### 2025-10-03 papers.qmd
add paper award
updates

## 2025
J. Adams, B. Berman, J. Michalenko, **J. D. Tucker**, "Conformal Anomaly Detection for Functional Data with Elastic Distance Metrics", *arXiv:2504.01172*, submitted, 2025. [arxiv preprint](https://arxiv.org/abs/2504.01172)

K. Goode, **J. D. Tucker**, D. Ries, and H. Hoffman, "An Explainable Pipeline for Machine Learning with Functional Data", *Computational Statistics and Data Analysis*, submitted, 2025. [arxiv preprint](https://arxiv.org/abs/2501.07602)

N. Winovich, L. Moynihan, O. Abdelrahman, R. West, S. Dauphin, **J. D. Tucker**, G. Huerta, K. Potter, R. Forrest, C. Phillips, and M. Ebeida, "VoroClust: Scalable Clustering for Remote Sensing", *IEEE Transactions on Geoscience and Remote Sensing*, in revision, 2024.

## 2024
J. E. Borgert, J. Hannig, **J. D. Tucker**, L. Arbeeva, A. N. Buck, Y. M. Golightly, S. P. Messier, A. E. Nelson, and J. S. Marron, "Elastic Shape Analysis of Movement Data", *JASA Case Studies and Applications*, submitted, 2024. [arxiv preprint](https://arxiv.org/abs/2409.13938)

A. Heiskala, **J. D. Tucker**, P. Choudhary, R. Nedelec, J. Ronkainen, O. Sarala, M. Järvelin, M. J. Sillanpääm, and S. Sebert, "Timing based clustering of childhood BMI trajectories reveal differential maturational patterns; Study in the Northern Finland Birth Cohorts 1966 and 1986", *International Journal of Obesity*, 10.1038/s41366-025-01714-8, 2024. [PDF](Papers/Heiskala_et_al-2025-International_Journal_of_Obesity.pdf)

@@

**J. D. Tucker** and D. Yarger, "Elastic Functional Changepoint Detection of Climate Impacts from Localized Sources", *Envirometrics*, 10.1002/env.2826, 2023. [PDF](Papers/Envirometics23_ElasticChangeDetection.pdf)

>>>>

## 2025
K. Goode, **J. D. Tucker**, D. Ries, and H. Hoffman, "An Explainable Pipeline for Machine Learning with Functional Data", *Journal of Data Science*, in revision, 2025. [arxiv preprint](https://arxiv.org/abs/2501.07602)

N. Winovich, L. Moynihan, O. Abdelrahman, R. West, S. Dauphin, **J. D. Tucker**, G. Huerta, K. Potter, R. Forrest, C. Phillips, and M. Ebeida, "VoroClust: Scalable Clustering for Remote Sensing", *IEEE Journal of Selected Topics in Applied Earth Observations and Remote Sensing*, submitted, 2024.

J. Adams, B. Berman, J. Michalenko, **J. D. Tucker**, "Conformal Anomaly Detection for Functional Data with Elastic Distance Metrics", *arXiv:2504.01172*, 2025. [arxiv preprint](https://arxiv.org/abs/2504.01172)

J. E. Borgert, J. Hannig, **J. D. Tucker**, L. Arbeeva, A. N. Buck, Y. M. Golightly, S. P. Messier, A. E. Nelson, and J. S. Marron, "Elastic Shape Analysis of Movement Data", *JASA Case Studies and Applications*, accepted, 2025. [arxiv preprint](https://arxiv.org/abs/2409.13938)

## 2024
A. Heiskala, **J. D. Tucker**, P. Choudhary, R. Nedelec, J. Ronkainen, O. Sarala, M. Järvelin, M. J. Sillanpääm, and S. Sebert, "Timing based clustering of childhood BMI trajectories reveal differential maturational patterns; Study in the Northern Finland Birth Cohorts 1966 and 1986", *International Journal of Obesity*, 10.1038/s41366-025-01714-8, 2024. [PDF](Papers/Heiskala_et_al-2025-International_Journal_of_Obesity.pdf)

@@

**J. D. Tucker** and D. Yarger, "Elastic Functional Changepoint Detection of Climate Impacts from Localized Sources", *Envirometrics*, 10.1002/env.2826, 2023. [PDF](Papers/Envirometics23_ElasticChangeDetection.pdf) **2024 Wiley-TIES Best Environmetrics Paper Award**
